---
title: "Getting Started"
description: | 
  Add a summary of R package & function usage to a Quarto document.
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

To add a summary table of package & function usage to the foot of a Quarto document, add `used_here()` to the end of the code. A separate code chunk with an appropriate heading is suggested but not essential.

The package author recommends using the [conflicted package](https://conflicted.r-lib.org) to resolve conflicts. In the example below, 'dplyr' has been preferred over stats for `filter()` and over the xts package for `last()`.

An alternative approach to using conflicted is to use the `exclude` or `include.only` argument in `library()`. This is also shown below with the xts version of `first` excluded and hence the dplyr version preferred.

## Some code

```{r setup}
options(tidyverse.quiet = TRUE)
library(conflicted)
library(dplyr)
library(tibble)
conflicts_prefer(dplyr::filter, dplyr::last)
library(usedthese)
library(xts, exclude = "first")

conflict_scout()
```

## More code

```{r}
tribble(~group, ~a1, ~a2, ~b1,
        "x", 1, 2, 3,
        "x", 4, 5, 6,
        "y", 7, 8, 9) |> 
  select(-starts_with("b")) |> 
  filter(group == "x") |> 
  mutate(first_a1 = first(a1),
         last_a2 = last(a2))
```

## Summary of usage

In the example below, `tribble()` is counted once against the (originating) tibble package even though it is also loaded by dplyr. And had we not used the conflicted package, `filter()` for example would have shown against the package name "dplyr, stats".

The rendered table is assigned the CSS class `.usedthese` to help other `used_*` functions find and aggregate multiple tables across one or more websites.

```{r warning=FALSE}

used_here()
```
