---
title: "Document usage"
description: | 
  Add a summary of R package & function usage to a Quarto document.
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Document usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In the example below, `tribble()` is counted once against the (originating) tibble package even though it is also loaded by dplyr. And `used_here()` assumes a loaded function is used rather than a base function of the same name, so `dplyr::filter()`, for example, is counted rather than `stats::filter()`.

Both the dplyr and xts packages have `first()` and `last()` functions. Because we've explicitly excluded `first()` in the library call for xts, the function is counted against dplyr. However, as there is no similar exclusion for `last()`, this is shown against both packages as a DUPE; a decision needs to be made as to which should be excluded. (`library()` can take an `exclude` character vector or an `include.only` vector.)

The rendered table is assigned the CSS class `.usedthese` to help other `used_*` functions find and aggregate multiple tables across one or more websites.

```{r setup}
options(tidyverse.quiet = TRUE)
library(tidyverse) 
library(usedthese)
library(xts, exclude = "first")

tribble(~group, ~a1, ~a2, ~b1,
        "x", 1, 2, 3,
        "x", 4, 5, 6,
        "y", 7, 8, 9) |> 
  select(-starts_with("b")) |> 
  filter(group == "x") |> 
  mutate(first_a1 = first(a1),
         last_a2 = last(a2))

used_here()
```
